\documentclass{article}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage[margin=0.8in]{geometry}

\setlength{\parskip}{\baselineskip}
\setlength{\parindent}{0pt}
\newcommand{\HRule}{\rule{\linewidth}{0.5mm}}
\newcommand{\Hrule}{\rule{\linewidth}{0.3mm}}

\makeatletter% since there's an at-sign (@) in the command name
\renewcommand{\@maketitle}{%
  \parindent=0pt% don't indent paragraphs in the title block
  \centering
  {\Large \bfseries\textsc{\@title}}
  \HRule\par%
  %\textit{\@author \hfill \@date}
  \par
}
\makeatother% resets the meaning of the at-sign (@)

\title{Letter of Motivation}
%\author{Shahriar Yazdipour}
%\date{MSc Applicant}

\begin{document}
  \maketitle% prints the title block
  \thispagestyle{empty}
  \vspace{16pt}

Dear Sir/Madam,

My name is Shahriar Yazdipour, and by this letter, I would like to express my interest to apply for a student visa for Germany to pursue my higher education. I have gained admission to the Technical University of Ilmenau for the master program titled as “Research in Computer Systems Engineering”, starting in October 2019.

I acquired a bachelor degree in Computer Science from the Kharazmi University of Tehran, which stands among the best academic institutes in Iran. Also, I have been working in this area for a year and have gained a lot of practical experience to solve real-world problems with my academic knowledge.

My interest in the boundless science of computer dates back to middle school, when I was  twelve and my father bought me a computer programming book as a birthday present; I was so fascinated by the book, which resulted in my huge obsession with programming and I was intoxicated by the feeling of satisfaction over being able to solve problems with my limited knowledge of programming, which thrived my thirst for wanting to extend my knowledge and brighten my horizons. Having a great motivation to study Computer Science, I got accepted at Kharazmi University (the very first university in my country - established in 1919). I was always able to achieve great grades and I was ranked first in exclusive courses. Also, I became a member of the University ACM/Olympiad team for four semesters and I have been chosen as a teacher assistant for many courses. But, importantly, with my excessive interest in technology, I had the opportunity to study many different fields of computer science and find the best major for my future study.

Meanwhile, I was able to get \textit{CCNA and Web-Security} Certificates from Beheshti University. And I was fortunate to pass a \textit{Deep Learning} course in Rajaee University. With all these experiences, I successfully publish my first international paper in “2017 International Conference on Machine Learning and Data Science, Delhi, India” with the help of my supervisor, Dr. Nahid Taherian. After university I joined a start-up, working on geographic systems in mobile devices. I learned various things and gained a great amount of experience from working as a team. After all these experiences, Now I know my favorite field of computer science and I am ready for a depth study.

When it comes to studying abroad, Germany is an attractive option due to a great number of reasonable grounds. First and foremost, the quality of education provided by German universities has been perfectly appreciated all around the world.
In addition, most of the universities in Germany are almost free of charge and this provides a great opportunity for foreign students to do a post-graduate degree in this country as living expenses are similar to their own home country. Finally, I am personally interested in studying in TU Ilmenau, because of successful experience my older university friends had with this university.

Considering Germany reputation for science and technology, and the esteemed status of the Ilmenau University of Technology with its talented faculty members and modern research facilities 
I strongly believe studying for a Masters degree in TU Ilmenau is the first step toward pursuing my dream of becoming a great value for my country and also Germany.

I am very much aware that I may have a hard time dealing with being away from my family, but I can assure you that I am absolutely motivated and totally prepare to attain my ambitions. Thank you very much indeed for giving me the opportunity to submit this application.

%\textit{\hfill )
Yours Faithfully,

Shahriar Yazdipour

\end{document}